Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2024-06-23 paper.qmd
Change linewidth and point size in MSE plots

mse_scurve_b <- ggplot(error_scurve, 
                     aes(x = b, 
                         y = log(MSE))) + 
  geom_point(size = 1) +
  geom_line() + 
  geom_vline(xintercept = 264, linetype="solid", 
             color = "black", linewidth=0.5, alpha = 0.5) +
  ylab("log(MSE)") +
  xlab("b") +
  ggtitle("(a)") +
  theme(aspect.ratio = 0.75,
        axis.text.x = element_text(size = 5),
        axis.text.y = element_text(size = 5),
        axis.title.x = element_text(size = 5),
        axis.title.y = element_text(size = 5, 
            angle=90),
        title = element_text(size = 36))
```

@@

mse_scurve_lwd <- ggplot(error_rm_scurve, 
                     aes(x = benchmark_rm_lwd, 
                         y = log(MSE))) + 
  geom_point(size = 1) +
  geom_line() + 
  geom_vline(xintercept = benchmark1, linetype="solid", 
             color = "black", linewidth=0.5, alpha = 0.5) +
  scale_x_continuous("standardized bin count", 
         transform = "reverse") + 
  ylab("log(MSE)") +
  ggtitle("(c)") +
  theme(aspect.ratio = 0.75,
        axis.text.x = element_text(size = 5),
        axis.text.y = element_text(size = 5),
        axis.title.x = element_text(size = 5),
        axis.title.y = element_text(size = 5, 
            angle=90),
        title = element_text(size = 36))
```

>>>>

mse_scurve_b <- ggplot(error_scurve, 
                     aes(x = b, 
                         y = log(MSE))) + 
  geom_point(
    size = 0.6
    ) +
  geom_line(
    linewidth = 0.3
    ) + 
  geom_vline(xintercept = 264, linetype="solid", 
             color = "black", linewidth=0.5, alpha = 0.5) +
  ylab("log(MSE)") +
  xlab("b") +
  ggtitle("(a)") +
  theme(aspect.ratio = 0.75,
        axis.text.x = element_text(size = 5),
        axis.text.y = element_text(size = 5),
        axis.title.x = element_text(size = 5),
        axis.title.y = element_text(size = 5, 
            angle=90),
        title = element_text(size = 36))
```

@@

mse_scurve_lwd <- ggplot(error_rm_scurve, 
                     aes(x = benchmark_rm_lwd, 
                         y = log(MSE))) + 
  geom_point(
    size = 0.6
    ) +
  geom_line(
    linewidth = 0.3
    ) + 
  geom_vline(xintercept = benchmark1, linetype="solid", 
             color = "black", linewidth=0.5, alpha = 0.5) +
  scale_x_continuous("standardized bin count", 
         transform = "reverse") + 
  ylab("log(MSE)") +
  ggtitle("(c)") +
  theme(aspect.ratio = 0.75,
        axis.text.x = element_text(size = 5),
        axis.text.y = element_text(size = 5),
        axis.title.x = element_text(size = 5),
        axis.title.y = element_text(size = 5, 
            angle=90),
        title = element_text(size = 36))
```
